Figures and supplemental figures for ecological resilience ms

### 2023-12-23 ms_figures_supp_figs.qmd
clean up supp figure plots

### Figure 3 - white noise check

Dispersal: no dispersal

Environmental noise: white noise

### Figure 4 - white noise check

Environmental noise: White

# 
# ggsave(filename = "output/tmp_figs/fig4-yield-white-noise-chk.png", plot = p1)
# ggsave(filename = "output/tmp_figs/fig4-biomass-white-noise-chk.png", plot = p2)

### Cabezon

```{r}
# # Set table names to be used to make the main figures
# 
# table_name_nd <- "no_dispersal_cabezon_mei_135_75"
# table_name_lp <- "larval_pool_cabezon_mei_135_75"
# table_name_nd_white <- "no_dispersal_abezon_white_135_75"
# table_name_lp_white <- "larval_pool_cabezon_white_135_75"
# 
# # Get meta data descriptins from the table names and the pretty 
# # versions for plotting
# 
# cab_mei_nd_current <- get_current_exp(table_name = table_name_nd)
# cab_mei_nd_nice <- get_nice_exp(table_name = table_name_nd)
# cab_white_nd_current <- get_current_exp(table_name = table_name_nd_white)
# cab_white_nd_nice <- get_nice_exp(table_name = table_name_nd_white)
# cab_mei_lp_current <- get_current_exp(table_name = table_name_lp)
# cab_mei_lp_nice <- get_nice_exp(table_name = table_name_lp)
# cab_white_lp_current <- get_current_exp(table_name = table_name_lp_white)
# cab_white_lp_nice <- get_nice_exp(table_name = table_name_lp_white)
#

### Figure 3 - MEI Cabezon

Species: Cabezon
#| label: figure_3
# 
# # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
# species_name <- cab_mei_nd_nice[[2]]
# brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
#                     sim_species_parms[[species_name]][["biom_exp"]]
# 
# brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
#                            waa_g = brf_waa_g)
# 
# # use functions to create useful data structures
# # FLEP to F reference tables by species
# spec_fleps_2_fs <-
#   get_fs_from_fleps(species = species_name,
#                     flep_inds = species_flep_fished_ind,
#                     f_vals =  fishing_mortality_values) 
# 
# ## Qry 
# qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
#               sum(number) as abundance,
#               sum(yield) as yield,
#               FROM '", table_name_nd, 
#               "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
#               GROUP BY sim_num, reserve_frac, flep_ratio, year, age
#               ORDER BY sim_num, reserve_frac, flep_ratio, year, age
#               ")
# 
# sim_res_out <- dbGetQuery(conn = con, qry)
# 
# #######
# 
# 
# ########### PIPELINING
# F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
#                                          fleps_2_fs = spec_fleps_2_fs)
# F_brf_maxes_yield
# 
# out_fs <- df_add_fs_out (input_df = sim_res_out,
#                          spec_fleps_2_fs = spec_fleps_2_fs,
#                          F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
# out_fs
# 
# med_yield <- get_median_yield(input_df = out_fs) 
# med_yield
# 
# med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
# med_biomass
# 
# out_yld_bm_sims_f_frac_yr <-
#   df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
#                                      age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use
# 
# # out_yld_bm_sims_f_frac_yr
# # pipeline works to here
# 
# sum_stats_f_frac_df <-
#   summary_stats_by_f_frac(
#     out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
#     median_yield = med_yield,
#     median_biomass = med_biomass
#   )
# sum_stats_f_frac_df
# 
# ## Plotting
# 
# p1 <- sum_stats_f_frac_df[[2]] %>%
#   filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
#   ggplot(.,
#        aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
#   metR::geom_contour_fill(bins = 12) + 
#   ggtitle(paste0(
#         cab_mei_nd_nice[[2]],
#         " ",
#         cab_mei_nd_nice[[1]],
#         " ",
#         cab_mei_nd_nice[[3]],
#         ":\nTime below median max yield"
#       )) +
#       xlab("Fraction of coastline in reserves") +
#       ylab("Harvest Rate (F/Fmsy)") +
#       scale_fill_viridis_c(option = "D", direction = -1) +
#       geom_segment(aes(
#         x = 0,
#         xend = max_reserve_frac,
#         y = 1,
#         yend = 1
#       ), colour = "black",
#       linetype = 2) +
#       scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
#       scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
#       theme_bw()
# 
# 
# p2 <- sum_stats_f_frac_df[[2]] %>%
#   filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
#   ggplot(.,
#        aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
#   metR::geom_contour_fill(bins = 12) +
#   ggtitle(paste0(
#         cab_mei_nd_nice[[2]],
#         " ",
#         cab_mei_nd_nice[[1]],
#         " ",
#         cab_mei_nd_nice[[3]],
#         ":\nTime below mean median biomass "
#       )) +
#       xlab("Fraction of coastline in reserves") +
#       ylab("Harvest Rate (F/Fmsy)") +
#       scale_fill_viridis_c(option = "D", direction = -1) +
#       geom_segment(aes(
#         x = 0,
#         xend = max_reserve_frac,
#         y = 1,
#         yend = 1
#       ), colour = "black",
#       linetype = 2) +
#       scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
#       scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
#       theme_bw()
# 
# print(p1)
# print(p2)

# ggsave(filename = "output/tmp_figs/fig3-yield-cab.png", plot = p1)
# ggsave(filename = "output/tmp_figs/fig3-biomass-cab.png", plot = p2)

### Better funcs

@@

########### PIPELINING

F_chr_nd_white_df_maxes_yield <- get_f_maxes_yield(input_df = chr_nd_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_chr)
F_chr_nd_white_df_maxes_yield

F_cab_nd_white_df_maxes_yield <- get_f_maxes_yield(input_df = cab_nd_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_cab)
F_cab_nd_white_df_maxes_yield

F_chr_lp_white_df_maxes_yield <- get_f_maxes_yield(input_df = chr_lp_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_chr)
F_chr_lp_white_df_maxes_yield

F_cab_lp_white_df_maxes_yield <- get_f_maxes_yield(input_df = cab_lp_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_cab)
F_cab_lp_white_df_maxes_yield

F_chr_nd_mei_df_maxes_yield <- get_f_maxes_yield(input_df = chr_nd_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_chr)
F_chr_nd_mei_df_maxes_yield

F_cab_nd_mei_df_maxes_yield <- get_f_maxes_yield(input_df = cab_nd_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_cab)
F_cab_nd_mei_df_maxes_yield

F_chr_lp_mei_df_maxes_yield <- get_f_maxes_yield(input_df = chr_lp_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_chr)
F_chr_lp_mei_df_maxes_yield

F_cab_lp_mei_df_maxes_yield <- get_f_maxes_yield(input_df = cab_lp_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_cab)
F_cab_lp_mei_df_maxes_yield

##----##
# No dispersal
# white
chr_nd_white_out_fs <- df_add_fs_out (input_df = chr_nd_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_nd_white_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)
chr_nd_white_out_fs[1:6,]

cab_nd_white_out_fs <- df_add_fs_out (input_df = cab_nd_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_nd_white_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)
cab_nd_white_out_fs[1:6,]
# enso
chr_nd_mei_out_fs <- df_add_fs_out (input_df = chr_nd_mei_df ,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_nd_mei_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)
chr_nd_mei_out_fs[1:6,]

cab_nd_mei_out_fs <- df_add_fs_out (input_df = cab_nd_mei_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_nd_mei_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)
cab_nd_mei_out_fs[1:6,]

# Larval pool
# white
chr_lp_white_out_fs <- df_add_fs_out (input_df = chr_lp_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_lp_white_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)
chr_lp_white_out_fs[1:6,]

cab_lp_white_out_fs <- df_add_fs_out (input_df = cab_lp_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_lp_white_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)
cab_lp_white_out_fs[1:6,]
# enso
chr_lp_mei_out_fs <- df_add_fs_out (input_df = chr_lp_mei_df ,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_lp_mei_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)
chr_lp_mei_out_fs[1:6,]

cab_lp_mei_out_fs <- df_add_fs_out (input_df = cab_lp_mei_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_lp_mei_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)
cab_lp_mei_out_fs[1:6,]

# White
# No dispersal
chr_nd_white_med_yield <- get_median_yield(input_df = chr_nd_white_out_fs) 
chr_nd_white_med_yield
cab_nd_white_med_yield <- get_median_yield(input_df = cab_nd_white_out_fs) 
cab_nd_white_med_yield
# larval pool dispersal 
chr_lp_white_med_yield <- get_median_yield(input_df = chr_lp_white_out_fs) 
chr_lp_white_med_yield
cab_lp_white_med_yield <- get_median_yield(input_df = cab_lp_white_out_fs) 
cab_lp_white_med_yield

# ENSO
# No dispersal
chr_nd_mei_med_yield <- get_median_yield(input_df = chr_nd_mei_out_fs) 
chr_nd_mei_med_yield
cab_nd_mei_med_yield <- get_median_yield(input_df = cab_nd_mei_out_fs) 
cab_nd_mei_med_yield
# larval pool dispersal
chr_lp_mei_med_yield <- get_median_yield(input_df = chr_lp_mei_out_fs) 
chr_lp_mei_med_yield
cab_lp_mei_med_yield <- get_median_yield(input_df = cab_lp_mei_out_fs) 
cab_lp_mei_med_yield

med_biomass <- get_median_biomass(input_df = out_fs)

# White
# No dispersal
chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs) 
chr_nd_white_med_biomass
cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs) 
cab_nd_white_med_biomass
# larval pool dispersal 
chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs) 
chr_lp_white_med_biomass
cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs) 
cab_lp_white_med_biomass

# ENSO
# No dispersal
chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs) 
chr_nd_mei_med_biomass
cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs) 
cab_nd_mei_med_biomass
# larval pool dispersal
chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs) 
chr_lp_mei_med_biomass
cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs) 
cab_lp_mei_med_biomass

@@

@@

@@

ggsave(filename = "output/tmp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.png", 
       plot = p_s1, 
       width = 12,
       height = 8)
ggsave(filename = "output/tmp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.svg", 
       plot = p_s1, 
       width = 12,
       height = 8)

@@

print(p_s2)
ggsave(filename = "output/tmp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.png", 
       plot = p_s2, 
       width = 12,
       height = 8)
ggsave(filename = "output/tmp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.svg", 
       plot = p_s2, 
       width = 12,
       height = 8)

@@

print(p_s3)
ggsave(filename = "output/tmp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.png", 
       plot = p_s3, 
       width = 12,
       height = 8)
ggsave(filename = "output/tmp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.svg", 
       plot = p_s3, 
       width = 12,
       height = 8)

>>>>

### Supplemental figure prep

@@

F_chr_nd_white_df_maxes_yield <- get_f_maxes_yield(input_df = chr_nd_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_chr)

F_cab_nd_white_df_maxes_yield <- get_f_maxes_yield(input_df = cab_nd_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_cab)

F_chr_lp_white_df_maxes_yield <- get_f_maxes_yield(input_df = chr_lp_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_chr)

F_cab_lp_white_df_maxes_yield <- get_f_maxes_yield(input_df = cab_lp_white_df,
                                         fleps_2_fs = spec_fleps_2_fs_cab)

F_chr_nd_mei_df_maxes_yield <- get_f_maxes_yield(input_df = chr_nd_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_chr)

F_cab_nd_mei_df_maxes_yield <- get_f_maxes_yield(input_df = cab_nd_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_cab)

F_chr_lp_mei_df_maxes_yield <- get_f_maxes_yield(input_df = chr_lp_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_chr)

F_cab_lp_mei_df_maxes_yield <- get_f_maxes_yield(input_df = cab_lp_mei_df, 
                                                 fleps_2_fs = spec_fleps_2_fs_cab)

##----##
# No dispersal
# white
chr_nd_white_out_fs <- df_add_fs_out (input_df = chr_nd_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_nd_white_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)

cab_nd_white_out_fs <- df_add_fs_out (input_df = cab_nd_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_nd_white_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)
# enso
chr_nd_mei_out_fs <- df_add_fs_out (input_df = chr_nd_mei_df ,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_nd_mei_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)

cab_nd_mei_out_fs <- df_add_fs_out (input_df = cab_nd_mei_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_nd_mei_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)

# Larval pool
# white
chr_lp_white_out_fs <- df_add_fs_out (input_df = chr_lp_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_lp_white_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)

cab_lp_white_out_fs <- df_add_fs_out (input_df = cab_lp_white_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_lp_white_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)

# enso
chr_lp_mei_out_fs <- df_add_fs_out (input_df = chr_lp_mei_df ,
                         spec_fleps_2_fs = spec_fleps_2_fs_chr,
                         F_maxes_yield = F_chr_lp_mei_df_maxes_yield, 
                         waa_g_df = chr_waa_g_df)

cab_lp_mei_out_fs <- df_add_fs_out (input_df = cab_lp_mei_df,
                         spec_fleps_2_fs = spec_fleps_2_fs_cab,
                         F_maxes_yield = F_cab_lp_mei_df_maxes_yield, 
                         waa_g_df = cab_waa_g_df)

# White
# No dispersal
chr_nd_white_med_yield <- get_median_yield(input_df = chr_nd_white_out_fs)

cab_nd_white_med_yield <- get_median_yield(input_df = cab_nd_white_out_fs)

# larval pool dispersal 
chr_lp_white_med_yield <- get_median_yield(input_df = chr_lp_white_out_fs)

cab_lp_white_med_yield <- get_median_yield(input_df = cab_lp_white_out_fs)

# ENSO
# No dispersal
chr_nd_mei_med_yield <- get_median_yield(input_df = chr_nd_mei_out_fs)

cab_nd_mei_med_yield <- get_median_yield(input_df = cab_nd_mei_out_fs)

# larval pool dispersal
chr_lp_mei_med_yield <- get_median_yield(input_df = chr_lp_mei_out_fs)

cab_lp_mei_med_yield <- get_median_yield(input_df = cab_lp_mei_out_fs)

# White
# No dispersal
chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs)

cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs)

chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs)

cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs)

# ENSO
# No dispersal
chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs)

cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs)

# larval pool dispersal
chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs)

cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs)

@@

p1 <-
  plot_contour_bm_below_thresh(sum_stats_f_frac_df = ,
                               spec_disp_noise = )

p2 <-
  plot_contour_yld_below_thresh(sum_stats_f_frac_df = ,
                                spec_disp_noise = )

@@

F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
                                         fleps_2_fs = spec_fleps_2_fs)
F_brf_maxes_yield

@@

ggsave(filename = "output/supp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.png", 
       plot = p_s1, 
       width = 12,
       height = 8)
ggsave(filename = "output/supp_figs/sup_fig1-brf-biomass-yield-white-nd-lp.svg", 
       plot = p_s1, 
       width = 12,
       height = 8)

@@

print(p_s2)
ggsave(filename = "output/supp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.png", 
       plot = p_s2, 
       width = 12,
       height = 8)
ggsave(filename = "output/supp_figs/sup-fig2-cab-chr-nodisp-mei-yld-biom.svg", 
       plot = p_s2, 
       width = 12,
       height = 8)

@@

print(p_s3)
ggsave(filename = "output/supp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.png", 
       plot = p_s3, 
       width = 12,
       height = 8)
ggsave(filename = "output/supp_figs/sup-fig3-cab-chr-lp-disp-mei-yld-biom.svg", 
       plot = p_s3, 
       width = 12,
       height = 8)
